---
title: "index"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(dplyr)
library(ggplot2)
library(maps)
library(mapproj)
source("analysis.R") 
read.csv("https://raw.githubusercontent.com/vera-institute/incarceration-trends/master/incarceration_trends.csv")
```


## An Introduction 
As an introduction, I wanted to look at how black people ages 15-64 have been incarcerated impacted in this country. Whether it be in a specific state, county, the country overall, I am interested to learn how people who look like me have been incarcerated in this country and to see if there is a correlation between their
incarceration and other races.
## Summary Information
```{r echo=FALSE}
summary_info
```
The highest fips takes place in Weston County. At the same time, the state that
has the highest fips is Wyoming. I was interested in this to see if black people
are greatly incarcerated in that state however they are not. The max black pop.
is 1289546. That is an extremely big number and makes me become inclined to 
assume in all large populations, black people greatly populate it. The state 
that has the max black people incarcerated is New York however the county that
has the most black people incarcerated is Los Angeles County. That is interesting
and makes me want to further research why that is.

## Trend over Time Chart
```{r state_inmate_prop, echo = FALSE}
ggplot(data = state_inmate_prop, aes(x = states, 
                                                  y = black_jail_pop_rate)) +
 geom_boxplot(outlier.shape = NA) +
 ylim(NA, 10000) +
labs(title = "Different States Black Jail Populations", x = "States", 
     y = "Rate per 100,000")
```
For trends over time, I created a boxplot that compares two states black jail 
populations. The two states I chose were Kentucky and Texas. As can be seen in 
graphic, Texas's median is smaller than Kentucky's lowest quartile. This 
highlights that kentucky's black population in jail is significantly larger
than Texas' even though Texas is the largest populated state in America. This 
can be done for all states.


## My MAP
The map illustrates the counties in a specific state that have a high population of black people incarcerated. Depending on the percentage, a specfic county will stand out more than others. 

```{r perc_black_15to64, echo = FALSE}
 ggplot(map_data) +
  geom_polygon(
    mapping = aes(x = long, y = lat, group = group, fill = black_perc_15to64),
    color = "white", size = 0.2
  ) +
  coord_map() +
  scale_fill_continuous(limits = c(0, max(map_data$black_perc_15to64)), 
                        na.value = "white") +
  blank_theme +
  ggtitle("Populations per county in TX")
```
